Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-02 files/Overview.tex
Overview v2

\subsubsection{Chapter 3}
In this chapter, some theory for the Finite Element Method is discussed. This chapter contains two parts, that covers two different results. The first result is the convergence of the Galerkin approximation of a general vibration problem. This result is presented in the article \cite{BV13}. The second result concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method. This result is presented in the textbook \cite{SF97}. In the first section, the authors continue with the general vibration problem that is used in chapter 2. The general vibration problem has a solution as shown in chapter 2. The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method. This oridinary differential equation can be proven to have a unique solution. The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem. The approach of the authors is to calculate the error estimates. The error is split into two parts, a semi-discrete and a fully discrete problem. Two assumptions are added to the assumptions from chapter 2. Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.

@@

In this chapter, two convergence results relating to the Finite Element Method are discussed. The first result is the convergence of the Galerkin approximation for vibration problems. This is presented in the article \cite{BV13.} For this result, the general variational form of chapter 2 is used. The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices. The article \cite{BV13} derive an error estimate for the solution of the general vartiational problem and the solution to it's Galerkin approximation. To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem. Following the assumptions, the authors prove error estimates for the semi-dicrete and the fully-discrete problem.\\

>>>>

\subsubsection{Chapter 3}
In this chapter, some theory for the Finite Element Method is discussed. This chapter contains two parts, that covers two different results. The first result is the convergence of the Galerkin approximation of a general vibration problem. This result is presented in the article \cite{BV13}. The second result concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method. This result is presented in the textbook \cite{SF97}. In the first section, the authors continue with the general vibration problem that is used in Chapter 2. The general vibration problem has a solution as shown in Chapter 2. The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method. This oridinary differential equation can be proven to have a unique solution. The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem. The approach of the authors is to calculate the error estimates. The error is split into two parts, a semi-discrete and a fully discrete problem. Two assumptions are added to the assumptions from Chapter 2. Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.

@@

In this chapter, two convergence results relating to the Finite Element Method are discussed. The first result is the convergence of the Galerkin approximation for vibration problems. This is presented in the article \cite{BV13.} For this result, the general variational form of Chapter 2 is used. The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices. The article \cite{BV13} derive an error estimate for the solution of the general vartiational problem and the solution to it's Galerkin approximation. To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem. Following the assumptions, the authors prove error estimates for the semi-dicrete and the fully-discrete problem.\\
